Tools for reproducible ex-post survey data harmonization

### 2020-07-10 data-raw/article.Rmd
update article

The increasing availability of microdata creates new opportunities for joint exploitation of these resources for comparative research. Before joint analysis is possible, the data need to be harmonized, i.e. transformed and combined in a single data set in a way that matches the measurement of the same characteristics and standardizes the coding of responses. We introduce the surveyharmonization and eurobarometer packages that help the reproducible ex-post harmonization of survey data stored in various, individual files with rich metadata.  We illustrate the proposed workflow using the case of the Eurobarometer surveys, which provide rich data on European publics in form of single-wave SPSS files from a period of over 25 years. Our tools are flexible and can be applied to other survey projects.

@@

In the case of the Eurobarometer, the harmonization process in greatly facilitated by the fact that all Eurobarometer waves are part of the same project with largely standardized procedures for many stages of the survey process, including questionnaire design, sampling, fieldwork, data processing and dissemination. Additionally, within each Eurobarometer wave, data for all countries are harmonized *ex ante*. Thus, in this case the harmonization of the data across multiple Eurobarometer surveys boils down to data data transformation and documentation. For the purposes of presenting the process of harmonization with surveyharmonization and eurobarometer packages, we use the case of the Eurobarometer without the loss of generality of the described procedures, since it includes all data processing steps involved in harmonization.

>>>>

The increasing availability of microdata creates new opportunities for joint exploitation of these resources for comparative research. Before joint analysis is possible, the data need to be harmonized, i.e. transformed and combined in a single data set in a way that matches the measurement of the same characteristics and standardizes the coding of responses. We introduce the `retroharmonize` and `eurobarometer` packages that help the reproducible ex-post harmonization of survey data stored in various, individual files with rich metadata.  We illustrate the proposed workflow using the case of the Eurobarometer surveys, which provide rich data on European publics in form of single-wave SPSS files from a period of over 25 years. Our tools are flexible and can be applied to other survey projects.

@@

In the case of the Eurobarometer, the harmonization process in greatly facilitated by the fact that all Eurobarometer waves are part of the same project with largely standardized procedures for many stages of the survey process, including questionnaire design, sampling, fieldwork, data processing and dissemination. Additionally, within each Eurobarometer wave, data for all countries are harmonized *ex ante*. Thus, in this case the harmonization of the data across multiple Eurobarometer surveys boils down to data data transformation and documentation. For the purposes of presenting the process of harmonization with `retroharmonize` and eurobarometer packages, we use the case of the Eurobarometer without the loss of generality of the described procedures, since it includes all data processing steps involved in harmonization.
